gij bent 2

### 2025-10-01 paper/paper.qmd
Better integrate Julie's part into the main text

When it comes to research of said shared code, things become more complicated. It is impossible for researchers to know the complete code of *all* language users in a language system. This situation forces models of language into necessary generalisations. Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian [@zipf_psycho-biology_1965] A-curve [as suggested by @kretzschmar_language_2015]. The make-up of this curve, with the most popular forms capturing most of the language use anyway, makes it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users. Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds. We see this, for example, in probabilistic grammar, the branch of variation studies that investigates how variation reflects competing constraints on linguistic choices [@grafmiller_general_2018]. Still, on a theoretical level, it is regrettable that models of variation do not start from the lowest common denominator of this variation: the language user.

@@

Contrastively, the advent of social media offers a unique opportunity for variationist research. Social media platforms offer an insight into the language systems of a large number of people.  Whereas previously it was possible to gauge the linguistic profile of only a small group of people [e.g. @labov_study_1968;@milroy_belfast_1978], social media offer linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [@vandekerckhove_perception_2007, 255]. In addition, social media data of course do not provide access to *all* of language for *all* users of a language system; not all utterances are made on social media, nor are all language users active on social media platforms. Nevertheless, social media platforms bring us closer to the idea of studying language *inside out*, starting from individual language users' variation, even if it is only for a single alternation among a subset of language users. This brings us to the first research question of this study:

1. What affordances does a focus on individual variation bring us in the context of alternation research, especially in contrast to traditional, aggregated alternation research?

@@

It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals. While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers. This is why both from a usage-based and a cognitive-linguistic perspective, the individual should be the primary unit of linguistic analysis where possible. Recent studies into individual variation in language use reveal that linguistic behavior is not uniformly progressive or conservative, either within individuals or among groups [@nevalainen_diffusion_2011]. While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [@petre_real-time_2018]. There is also variation in the language-internal factors influencing language change. While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [@fonteyn_individuality_2020]. Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [@fonteyn_probability_2022]. Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [@guy_cognitive_2013;@zenner_individual_2016;@van_den_stock_individual_2024].

>>>>

When it comes to research of said shared code, things become more complicated. It is impossible for researchers to know the complete code of *all* language users in a language system. This situation forces models of language into necessary generalisations. Generalisation is a valid strategy, as most linguistic variation, when tallied at large, will lead to a Zipfian [@zipf_psycho-biology_1965] A-curve [as suggested by @kretzschmar_language_2015]. The make-up of this curve, with the most popular forms capturing most of the language use anyway, makes it so the "general" behaviour of language variation that is typically captured in corpora also represents a fair share of what would be the individual code of most language users. Of course, there are factors influencing what language forms are used,[^lects] but broadly speaking, this generalisation holds.

@@

Still, this does not mean that language users necessarily all behave in the same way. @nevalainen_diffusion_2011 show that linguistic behaviour is not uniformly progressive or conservative, either within individuals or among groups. While later-born authors often show more progressive tendencies, there is notable individual variation even within generational cohorts [@petre_real-time_2018]. There is also variation in the language-internal factors influencing language change. While most language-internal factors are broadly shared, less influential factors reveal personal differences in usage [@fonteyn_individuality_2020]. Moreover, some individuals are more adaptable to linguistic change over their lifetimes, while others remain stable or even deviate in the opposite direction [@fonteyn_probability_2022]. Personality traits also play a role, affecting how individuals adopt or evaluate new linguistic features [@guy_cognitive_2013;@zenner_individual_2016;@van_den_stock_individual_2024].

Most studies concerning individual variation involve an analysis of historical data, or are based on smaller-scale surveys [e.g. @labov_study_1968;@milroy_belfast_1978]. Contrastively, the advent of social media offers a unique opportunity for variationist research. Social media platforms offer an insight into the language systems of a large number of people, offering linguistic variation at an unprecedented scale.[^c-clamp] While one should not consider spoken and written social media as equivalent, social media language has nonetheless proven a useful proxy for the former [@vandekerckhove_perception_2007, 255]. In addition, social media data of course do not provide access to *all* of language for *all* users of a language system; not all utterances are made on social media, nor are all language users active on social media platforms. Nevertheless, social media platforms bring us closer to the idea of studying language *inside out*, starting from individual language users' variation, even if it is only for a single alternation among a subset of language users. This brings us to the first research question of this study:

1. What affordances does a focus on individual variation bring us in the context of contemporary alternation research, especially in contrast to traditional, aggregated alternation research?

@@

It is essential to recognize that the widespread changes observed across entire populations ultimately stem from changes that begin within individuals. While linguistic changes may eventually become collective phenomena, their origins lie in the minds and speech of individual speakers. This is why both from a usage-based and a cognitive-linguistic perspective, the individual should be the primary unit of linguistic analysis where possible.
